Omics-based Single Step Trait Prediction

### 2017-03-24 paper/manuscript.tex
Update plot legends for manuscript

\section*{Results}

@@

@@

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/maizego_admixture_pca.pdf}
\caption{
  (\textbf{A}) Ancestry coefficients for 211 tropical/subtropical inbred lines
  from the maize diversity panel considering $K=2 \dots 5$ ancestral
  populations.
  (\textbf{B}) Principal component analysis for nine different core sets of the
  set of tropical/subtropical maize inbred lines.
  For each size of the core set, its members are plotted as orange dots whereas 
  all genotypes that are not elements of the cores sets (\textit{i.e.},
  'Complement') are depicted as blue dots.
}
\label{fig:PopStructure}
\end{figure}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:16:30 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids. As predictors, pedigree (P), genomic (G), transcriptomic (T) data and combinations thereof we used.} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
P & 0.54 (0.049) & 0.48 (0.052) & 0.21 (0.037) & 0.6 (0.019) & 0.35 (0.043) & 0.42 (0.117) \\ 
  G & 0.74 (0.052) & 0.63 (0.052) & 0.43 (0.036) & 0.65 (0.022) & 0.46 (0.046) & 0.47 (0.126) \\ 
  PG & 0.71 (0.054) & 0.57 (0.055) & 0.35 (0.038) & 0.62 (0.023) & 0.39 (0.048) & 0.42 (0.13) \\ 
  PT & 0.73 (0.056) & 0.53 (0.059) & 0.35 (0.04) & 0.61 (0.025) & 0.31 (0.05) & 0.37 (0.14) \\ 
  GT & 0.75 (0.053) & 0.61 (0.055) & 0.43 (0.037) & 0.65 (0.024) & 0.44 (0.048) & 0.44 (0.134) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
T & 0.75 (0.055) & 0.34 (0.062) & 0.4 (0.041) & 0.47 (0.029) & 0.16 (0.05) & 0.27 (0.145) \\ 
  P & 0.46 (0.047) & 0.53 (0.05) & 0.23 (0.037) & 0.46 (0.023) & 0.38 (0.039) & 0.34 (0.132) \\ 
  G & 0.67 (0.053) & 0.47 (0.055) & 0.43 (0.038) & 0.48 (0.027) & 0.36 (0.046) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 22 08:40:11 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel. As predictors, genomic (G) data, transcriptomic (T) data and their combination (GT) were used. The decimal after the predictor name indicates the size of the genetic material that was covered by inbred lines in the core set.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G\_Full & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT\_Full & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  GT\_0.2 & 0.35 (0.072) & 0.23 (0.1645) & 0.26 (0.0519) & 0.36 (0.0474) & 0.38 (0.0722) & 0.44 (0.0273) \\ 
  GT\_0.1 & 0.29 (0.0762) & 0.21 (0.1659) & 0.23 (0.0522) & 0.32 (0.0471) & 0.4 (0.0743) & 0.39 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

\Genetics2level{Some results section}

\Genetics2level{Another results section}

>>>>

\section*{Results}
\Genetics2level{Inbred lines}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 22 08:40:11 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\label{tbl:InbredTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel. As predictors, genomic (G) data, transcriptomic (T) data and their combination (GT) were used. The decimal after the predictor name indicates the size of the genetic material that was covered by inbred lines in the core set.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G\_Full & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT\_Full & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  GT\_0.2 & 0.35 (0.072) & 0.23 (0.1645) & 0.26 (0.0519) & 0.36 (0.0474) & 0.38 (0.0722) & 0.44 (0.0273) \\ 
  GT\_0.1 & 0.29 (0.0762) & 0.21 (0.1659) & 0.23 (0.0522) & 0.32 (0.0471) & 0.4 (0.0743) & 0.39 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

\Genetics2level{Hybrids}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:16:30 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\label{tbl:HybridTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids. As predictors, pedigree (P), genomic (G), transcriptomic (T) data and combinations thereof we used.} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
P & 0.54 (0.049) & 0.48 (0.052) & 0.21 (0.037) & 0.6 (0.019) & 0.35 (0.043) & 0.42 (0.117) \\ 
  G & 0.74 (0.052) & 0.63 (0.052) & 0.43 (0.036) & 0.65 (0.022) & 0.46 (0.046) & 0.47 (0.126) \\ 
  PG & 0.71 (0.054) & 0.57 (0.055) & 0.35 (0.038) & 0.62 (0.023) & 0.39 (0.048) & 0.42 (0.13) \\ 
  PT & 0.73 (0.056) & 0.53 (0.059) & 0.35 (0.04) & 0.61 (0.025) & 0.31 (0.05) & 0.37 (0.14) \\ 
  GT & 0.75 (0.053) & 0.61 (0.055) & 0.43 (0.037) & 0.65 (0.024) & 0.44 (0.048) & 0.44 (0.134) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
T & 0.75 (0.055) & 0.34 (0.062) & 0.4 (0.041) & 0.47 (0.029) & 0.16 (0.05) & 0.27 (0.145) \\ 
  P & 0.46 (0.047) & 0.53 (0.05) & 0.23 (0.037) & 0.46 (0.023) & 0.38 (0.039) & 0.34 (0.132) \\ 
  G & 0.67 (0.053) & 0.47 (0.055) & 0.43 (0.038) & 0.48 (0.027) & 0.36 (0.046) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

\Genetics2level{Coverage of the genetic space}

@@

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/maizego_core_sampling_pca.pdf}
\caption{
  Coverage of the genetic space by nine different core sets. 
  Genotypes are distributed according to their scores based on the first two
  principal components (PC).
  The total genetic space was spanned by 149 genotypes from the maize diversity 
  panel for which both, genomic and transcriptomic data, were available.
  Genotypes that were members of the core set (orange triangles) were declared 
  as being covered by both predictors whereas members of the complement (blue,
  filled circles) were declared as only being covered by genomic information.
  Assignments of genotypes to the core set was done by selecting a subset of
  genotypes that maximized the average genetic distance in the core set based 
  on the Modified Rogers distance between all genotypes.
  Core set sizes ranged from 10\% to 90\% of the 149 available genotypes and
  are given as decimals above each facet of the plot.
}
\label{fig:CoreSetPCA}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/maizego_admixture_k3_pca.pdf}
\caption{
  Population structure of 149 maize inbred lines from the maize diversity panel
  covered by genomic and transcriptomic data.
  (\textbf{A}) Ancestry coefficients from an admixture analysis when 
  considering $K=3$ ancestral populations.
  (\textbf{B}) Principal component analysis with genotypes colored according to 
  the most likely ancestral population (\textit{i.e.}, share $\geq 0.5$) as 
  indicated by the admixture analysis.
  Genotypes for which none of the three ancestry coefficients reached a value
  of 0.5 were classified as "mixed".
}
\label{fig:PopStructure}
\end{figure}

@@
